Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-31 Response/Response 2/response-2.tex

However, if we perform the distributed algorithms for significantly enough to ensure strict monotonicity of the objective, then the overall of convergence of Algorithm 2 is guaranteed by following the arguments in [27]. Note that in addition, uniqueness of the limit point is also necessary for the sequence convergence. It can be assured by regularizing the original convex objective with a quadratic term as in (46b) in each \ac{SCA} step to guarantee strong convexity, and thereby ensuring a unique minimizer and limit point.

Additionally, to reduce the signaling overhead involved with the information exchange due to multiple loops, we can also combine the \ac{MMSE} receiver update in (23b) after each \ac{SCA} step for the transmit precoders. If in addition \eqn{J_{\max}} is sufficiently large, then the strict monotonicity of the objective sequence is still ensured by the combined update. It follows from the fact that the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained after each \ac{SCA} update. The newly found solution is also feasible and the objective improves monotonically in strict sense. Therefore, if the above conditions are satisfied, then the convergence of the sequence of iterates is guaranteed.

For our simulation scenario, we have fixed the maximum number of \ac{ADMM} iterations in each \ac{SCA} step as \eqn{J_{\max} = 20}. Note that it is sufficient to ensure strict monotonic decrease of the objective value in each \ac{SCA} step. However, the number of iterations to ensure strict monotonicity of the objective depends on the problem under consideration. The practical significance of limited number of \ac{ADMM} iterations is discussed briefly in [10, Section 3.2.2].

Regarding the specific comments related to the \ac{ADMM} convergence for subproblem (20), we provide the following remarks by considering that the objective is regularized by a quadratic term as discussed in Appendix A-B to ensure strongly convexity.

\begin{enumerate}
\item The primal objective and the augmented Lagrangian are strongly convex, therefore, the optimal solution exists and is unique in the feasible convex set of subproblem (20). It follows from that the \ac{ADMM} algorithm converges to a unique limit point, which is a fixed point of the iterative \ac{ADMM} algorithm.

\item In general, the fixed point of the subproblem (20) is not unique. It is due to the fact that the original objective is convex, and therefore it can have multiple solutions in the feasible convex set. Therefore, the \ac{ADMM} algorithm can have a set of fixed points in the feasible set. However, if we regularize the objective with a strongly convex quadratic term as discussed in Appendix A-B, then the distributed approach finds a fixed point of the original convex subproblem.

\item By using previous argument, any fixed point of the algorithm is a solution for the problem (20), since the original convex objective can have multiple solutions. The particular choice of the fixed point of the \ac{ADMM} approach depends on the operating point used in the regularization term in the objective.

@@

\item Upon convergence of the \ac{ADMM} approach, the interference vector is guaranteed to be equal to the actual interference seen in the network. This is the main principle of \ac{ADMM} where the local variables (the vectors in (38)) converge to the global variables, which are the actual inference vectors.

However, to answer the reviewer questions in relation to the overall convergence of the distributed method presented in Algorithm 2, we consider the following conditions are satisfied in each \ac{SCA} update step.
\begin{itemize}
	\item The objective function is regularized by a quadratic term as discussed in Appendix A-B to ensure strict convexity of the objective function, which leads to the uniqueness of the solution.
	\item The distributed algorithms are performed until convergence or for sufficient number of iterations to ensure strict monotonic decrease of the objective sequence.
\end{itemize}
Upon satisfying the above conditions, even if we update the receive beamformers using the \ac{MMSE} receiver in (23b) after each \ac{SCA} step for solving the transmit precoders, strict monotonicity is still ensured. It follows from the fact that the \ac{MMSE} receivers are optimal for the fixed transmit precoders, and therefore the objective sequence decreases monotonically after each update in strict sense.

\begin{enumerate}
	\item Since the above conditions are satisfied by Algorithm 2, then the existence of a fixed point for Algorithm 2 is guaranteed by following the arguments in [27].

	\item In general, fixed point of Algorithm 2 is not unique. Note that the iterative nature of the \ac{SCA} approach is based on approximating the nonconvex constraint by a convex one around some fixed operating point. While initializing the iterative Algorithm 2, we need to find a fixed operating point upon which the convex function is approximated. Therefore, depending on the choice of initial feasible point, the algorithm terminates at different fixed point upon convergence. Hence, there exist a set of fixed points for Algorithm 2.

	\item The nonconvex problem (16) can have multiple stationary points and the iterative method proposed in Algorithm 2 finds a stationary point of the nonconvex problem. Therefore, all fixed points found by Algorithm 2 upon convergence are indeed the stationary points of the original nonconvex problem.

### 2015-07-31 Report/dual_approach.tex
updated

Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{j}} iteration as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right \|^2 \eqsub \eqspace \\
\text{subject to} &\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\quad&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\quad& \sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
&\quad& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}
}{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right \|^2 \eqsub \eqspace \\
&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}}
where \me{\mbfa{\zeta}^{(j)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(j)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{j}} iteration as
\begin{equation} \label{const-admm1}
\mbfa{\zeta}_b = \mbfa{\zeta}^{(j)}_b.
\end{equation}

@@

\mbfa{\nu}_b^{(j+1)} = \mbfa{\nu}_b^{(j)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(j+1)} \right )

@@

where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration. The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}. In numerical simulations, we consider step size \me{\rho=2}. The above iterative procedure is performed until convergence or terminated when exceeding a predetermined number of iterations, say, \eqn{J_{\max}}. The \ac{ADMM} based precoder design is outlined in Algorithm \ref{algo-3}.

@@

			send precoded downlink pilot with \me{\mbf{m}}\;
			evaluate \me{\mvec{w}{l,k,n}} at each user and inform to all \acp{BS} in \eqn{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective} \;

@@

The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}. \review{To reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}. If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence. However, if the distributed methods are performed for an adequate number of iterations to ensure the strict monotonicity of the objective sequence in each \ac{SCA} update, then the limit point of the sequence of iterates is a stationary point of the nonconvex problem \eqref{eqn-6}.} %Note that the receivers can also be updated together with the transmit precoders in each \ac{SCA} step, \textit{i.e.}, \eqn{K_{\max} = 1}, since the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained in each \ac{SCA} step.}

>>>>

Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{j}} iteration as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right \|^2 \eqsub \eqspace \\
\text{subject to} &\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\quad&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\quad& \sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
&\quad& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}
}{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
	&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b   ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b  ) +  \tfrac{\rho}{2}  \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b  \|^2 \eqsub \eqspace \\
	&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
	&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
	&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
	& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}
}
where \me{\mbfa{\zeta}^{(j)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(j)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{j}} iteration as
\begin{equation} \label{const-admm1}
\mbfa{\zeta}_b = \mbfa{\zeta}^{(j)}_b.
\end{equation}

@@

\mbfa{\nu}_b^{(j+1)} = \mbfa{\nu}_b^{(j)} + \rho \: (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(j+1)}  )

@@

where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model. The convergence rate is susceptible to the choice of step size parameter \me{\rho}. In numerical simulations, we consider step size \me{\rho=2}. The above iterative procedure is performed until convergence or terminated when exceeding a predetermined number of steps, say, \eqn{J_{\max}}. Algorithm \ref{algo-3} outlines a practical way of implementing the \ac{ADMM} based precoder design with minimal signaling overhead.

@@

			send precoded downlink pilot with \me{\mbf{m}_{l,k,n}}\;
			evaluate \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} at each user \;

@@

The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}. \review{To reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}. If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence. However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large to ensure strict monotonicity of the objective, then the convergence can be guaranteed (see Appendices \ref{sec-3.5} and \ref{sec-dist-conv}). Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.}

%	Additionally, if the receivers are updated together with the transmit precoders using \eqref{eqn-10} in each \ac{SCA} step, strict monotonicity is still ensured, since the \ac{MMSE} receivers are optimal for the fixed transmit precoders.}
%However, if the distributed methods are performed for an adequate number of iterations to ensure the strict monotonicity in each \ac{SCA} update, then the limit point of the sequence of iterates is a stationary point of the nonconvex problem \eqref{eqn-6}. Note that the receivers can also be updated together with the transmit precoders in each \ac{SCA} step, \textit{i.e.}, \eqn{K_{\max} = 1}, since the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained in each \ac{SCA} step.}

### 2015-07-31 Report/kkt_mse_approach.tex
updated

In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the global queue deviation objective with few number of iterations. \review{The alternative way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.}

>>>>

In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the queue deviation with few number of iterations. \review{The alternative way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.}
